Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-11-01 paper/results.tex
Several changes from the rebuttal.

\subsection{Forced Choice User Experiment}
We performed a user study to evaluate the forced choice error correction method among novices and experts. To be comparable to Haehn~\etal's Dojo user study~\cite{haehn_dojo_2014}, participants were asked to proofread the AC4 subvolume for 30 minutes. We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation with respect to the ground truth labeling (provided in \cite{haehn_dojo_2014}). For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations. Median VI $=0.476$ ($SD=0.089$), with mean VI $=0.512$ ($SD=0.09$). Most novices and all experts were able to improve upon this score with both focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).

@@

>>>>

\subsection{Forced Choice User Experiment}
We performed a user study to evaluate the forced choice error correction method among novices and experts. To be comparable to Haehn~\etal's Dojo user study~\cite{haehn_dojo_2014}, participants were asked to proofread the AC4 subvolume for 30 minutes. We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation with respect to the ground truth labeling (provided in \cite{haehn_dojo_2014}). For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations. 
%\CHANGED{Our hypothesis is that VI reduction is significantly better with GP than with other tools. For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}
\CHANGED{The initial segmentation yields a} median VI $=0.476$ ($SD=0.089$), with mean VI $=0.512$ ($SD=0.09$). Most novices and all experts were able to improve upon this score with both focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).

@@

\CHANGED{\paragraph{Confirmatory Data Analysis.} We use a single factor between-subject design with the factor being the proofreading method (GP, FP, or Dojo). Our hypothesis is that VI reduction is significantly better with GP than with other tools. For this, we treat VI as a continuous variable and use analysis of variance (ANOVA) followed by parametric tests (Welch's t-test).}

\CHANGED{\emph{AC4 subvolume.} For novice performance, we observe a significant effect ($\alpha = 0.05$) of which proofreading tool is used for the three conditions GP, FP, and Dojo [$F(2,27) = 6.446, p = 0.005$] when comparing the mean VI outcome. Post hoc comparisons (after Bonferroni correction) indicate that the mean VI for GP is significantly lower than for FP [$t_{27} = -2.7696, p = 0.0168$], and that the mean VI for GP is significantly lower than for Dojo [$t_{27} = -4.407, p < 0.001$]. This means that novices using GP perform significantly better than using FP and Dojo. 
A similar trend is visible when comparing the expert performance between GP and FP as the change in mean VI of GP is significantly better ([$F(1,18) = 7.054, p = 0.016$] and [$t_{18} = -2.6559, p = 0.0216$]). For automatic selection with threshold, the difference in mean VI is very large and GP also performs significantly better ([$F(1,18) = 89.902, p < 0.001$] and [$t_{18} = 9.482, p < 0.001$]). The final VI scores of the selection oracle with GP and FP are very similar and the difference between them is not significant [$F(1,18) = 0.795, p = 0.384$]. However, the VI reduction rate of GP is much higher as seen in Fig.~\ref{fig:ac4trails} (right).}

\CHANGED{\emph{L. Cylinder.} The automatic selection with threshold yields similar results as on the other dataset and we observe a significant improvement when using GP instead of FP ([$F(1,98) = 26.676, p < 0.001$], post hoc comparison [$t_{98} = 5.1648, p < 0.001$]). The selection oracles of GP and FP result in very similar final VI scores and the difference is not significant [$F(1,98) = 0.071, p = 0.790$], but GP reaches minimum VI faster in $10,000$ corrections versus FP in $26,170$ corrections.}
